### 2012-04-12 docs/unit_tests/unit_tests.tex
spacing

In addition to the \maestro science problems, which use the full
capabilities of \maestro, there are a number of unit tests that
exercise only specific components of the \maestro\ solvers.  These
tests have their own drivers (a custom {\tt varden.f90}) that
initialize only the data needed for the specific test and call
specific \maestro\ routines directly.

>>>>

In addition to the \maestro\ science problems, which use the full
capabilities of \maestro, there are a number of unit tests that
exercise only specific components of the \maestro\ solvers.  These
tests have their own drivers (a custom {\tt varden.f90}) that
initialize only the data needed for the specific test and call
specific \maestro\ routines directly.
